Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-03-22 documentation/userguide.tex

for period in 25.0 50.0 75.0 100.0
do
  dir=results/period$period/
  castro_rotational_period=$period
  stop_time=$period
  run $dir $nprocs $walltime
done
\end{lstlisting}%$
This will create the subdirectories \texttt{results/period25.0} through \texttt{results/period100.0}
and in each directory the inputs file will have the corresponding \texttt{castro.rotational\_period}.
Each job will stop after one rotational period has been completed. When all have been completed, you should 
type \texttt{bash run.sh} once more; this will move all output files (checkpoints, plot files, diagnostics)
to the \texttt{output/} subdirectory of that problem location, and on supported HPC systems will also copy these 
files to the long-term storage system (see Section \ref{sec:archiving} for more details). 
Generally our analysis scripts expect all the output to be in the 
\texttt{output/} subdirectory. Also, if the machine crashes before your run completes, running \texttt{bash run.sh}
again will automatically restart your job from the most recent checkpoint.

>>>>

for period in 25.0 50.0 75.0 100.0
do
  dir=results/period$period/
  castro_rotational_period=$period
  stop_time=$period
  run $dir $nprocs $walltime
done
\end{lstlisting}%$
This will create the subdirectories \texttt{results/period25.0} through \texttt{results/period100.0}
and in each directory the inputs file will have the corresponding \texttt{castro.rotational\_period}.
Each job will stop after one rotational period has been completed. At the end, the script will automatically move all 
output files (checkpoints, plot files, diagnostics)
to the \texttt{output/} subdirectory of that problem location, and on supported HPC systems will also copy these 
files to the long-term storage system (see Section \ref{sec:archiving} for more details). 
Generally our analysis scripts expect all the output to be in the 
\texttt{output/} subdirectory. Also, if the machine crashes before your run completes, running \texttt{bash run.sh}
again will automatically restart your job from the most recent checkpoint.

### 2015-03-22 papers/wdmerger_I/paper.tex

%\documentclass[12pt,preprint]{aastex}
\documentclass{emulateapj}
% for \sout
\usepackage{ulem}
% makes sure \em{} is italic rather than underlined (corrects ulem from line above)
\normalem

@@

The computational domain has a total size of $1.024 \times 10^{10}\ \text{cm}$ in each 
spatial dimension, and is centered at the origin. Our coarse grid has $256^3$ zones,
corresponding to a spatial resolution of 400 km. For the present study, we choose a simple 
refinement strategy: all zones within the Roche radius of each star are tagged for maximal 
refinement. We also ensure that the outer part of the domain is never tagged for refinement.
In future work we will add criteria that tag for refinement the gas between the stars, which is
expected to feature nuclear burning.

>>>>

%\documentclass[12pt,preprint]{aastex}
\documentclass[iop]{emulateapj}
% for \sout
\usepackage{ulem}
% makes sure \em{} is italic rather than underlined (corrects ulem from line above)
\normalem

% these lines seem necessary for pdflatex to get the paper size right
\pdfpagewidth 8.5in
\pdfpageheight 11.0in

@@

The computational domain has a total size of $1.024 \times 10^{10}\ \text{cm}$ in each 
spatial dimension, and is centered at the origin. Our coarse grid has $256^3$ zones,
corresponding to a spatial resolution of 400 km. For the present study, we choose a simple 
refinement strategy: all zones within twice the Roche radius of each star are tagged for maximal 
refinement. The extra buffer from doubling the size of this region ensures that the sharp density
gradients near the edge of the star are within the zone of refinement. We also ensure that the 
outer part of the domain is never tagged for refinement. In future work we will add criteria 
that tag for refinement the gas between the stars, which is expected to feature nuclear burning.
